What can GitHub and Googlecode Issues tell us about Exceptions in Android and Java?

### 2014-09-01 android-stacks.tex
improvements all over

\author{\IEEEauthorblockN{Roberta Coelho\IEEEauthorrefmark{1},
Georgios Gousios\IEEEauthorrefmark{2}, 
Arie van Deursen\IEEEauthorrefmark{2},
Lucas Almeida\IEEEauthorrefmark{1}
}
\IEEEauthorblockA{\IEEEauthorrefmark{1}Federal University of Rio Grande do Norte\\
Natal, Brazil\\
Email: \texttt{roberta@dimap.ufrn.br,lucas.almeida@ppgsc.ufrn.br}}
\IEEEauthorblockA{\IEEEauthorrefmark{2}Delft University of Technology\\
Delft, The Netherlands\\
Email: \texttt{\{g.gousios,arie.vandeursen\}@tudelft.nl}}
}

@@

This paper reports a repository mining study which analyzed all the issues created on
Android projects available in GitHub (482 applications) and Google code (157 applications)
Overall, our research set includes 32,582 issues in GitHub and 41,674 issues in Googlecode from which (4,208)  (1,986) in GC stack traces 
were extracted. Such stack traces were distilled and analyzed in 
combination with source code and bytecode analysis. This study 
consistently identifies common characteristics of reported 
exception stacks traces - e.g., the NullPointerException was the reported cause 
on 30,08\% of all analyzed exception stack traces, and was mentioned in approximately 
50\% of all projects analyzed. Moreover,  the cross-project analysis 
of exception stack traces enabled to consistently reveal   
fragilities of the exception-related code: 
(1) undocumented runtime exceptions signaled by third party code,
(2) undocumented checked exceptions thrown by Android native code
(3) unexpected exception wrappings (e.g., Errors being wrapped in checked exceptions) 
revealing that Java hybrid exception model is not fully used according to its purpose.
Such fragilities impose challenges to application robustness not only 
in Android environment but also to other systems based on Java exception model.

@@

To do so we perform a post mortem analysis of the exception stack traces embedded on all issues
created on Android projects available in GitHub and Googlecode. Using a custom tool called ExceptionMiner,
 which we develop specifically for this study, we mine stack traces from issues across all Android projects on
GitHub and Googlecode. Overall, we analyzed the XXXX issues extracted from on XXX Android projects defined in
GitHub and XXX projects defined in Googlecode. From these issues,  XXX stack traces were extracted and used as
 a source of information for our analysis. The stack trace analysis was augmented by additional information
extracted from JDK, Android SO and Android SDK and the applications using byte code and source code analysis.
 Manual inspection was used to leverage the understanding of exception stack traces and support further discussions and insights.

@@

This set of 482 projects contained overall 32,582 issues from which 4,208 exception stack traces 
were extracted. Issues on Github are different from issues on dedicated bug tracking tools such as 
Bugzilla and Jira. The most important difference is that there are no predefined fields
  (e.g. severity and priority). Instead, Github uses a more open ended tagging system, on which
repositories are offered a pre-defined set of labels, but repository owners can modify 
them at will. Therefore, an issue may have none ore an arbitrary set of labels depending 
on which repository it was created.

@@

To identify Android projects in Googlecode, we performed a similar heuristic, we performed a case insensitive search 
(on Googlecode search interface) for the term \textsf{android}.  On January 2014, when we queried Googlecode, such heuristic could
 find 788  projects, from which 724 defined at least 1 issue and, 183 projects 
had at least one issue including a stack trace. Then we performed further cleanup, inspecting the site of every Android
reporting at least one stack trace, and as a result we could identify 157. 
Android projects.  From this set all issues (41,674) were analyzed and 1,986 stack traces were extracted.

@@

\noindent\emph{Exception Stack Trace Distiller.} 
Distills the information that composes a stack trace and storing the results in a
relational database. Some of the information extracted from the stack traces were:
 the exception being thrown, its signaler, the exception root cause, its corresponding signaler,
and packages related to each one of these fields.
The tool is based on a combination between a regular expression based parser 
with heuristics able to identify and filter exception names and stack traces inline with text. In
contrast to existing issue parsing solutions such as Infozilla, the parser
created in this work can extract all causes related to an exception on a stack,
and stack traces embedded in logs files.
AS PRESENTED IN FIGURE X

@@

\subsection{Manual Inspections}
This study was also based in a set of manual inspection tasks. Besides the 
 identification of Android projects details previously. 
Manual inspections were used discover the type of exceptions thrown by 
the applications and libraries we manually inspect the sourcecode or javadoc
 documentation of each of them. When the exception was removed from the 
last app version, the previous versions were analyzed. When the exception was
 not found on the previous versions, the exception was discarded.  Only 31 exceptions 
remained undefined which were reported on 61 exception stack traces (as presented in Table ~\ref{tab:typeroottab}).

@@

After distilling the information available on the exception stack traces we could find 
the the exceptions commonly reported as the root causes of stack traces.
Table \ref{tab:toptenandroid} illustrates the top 10 root causes found in the study,
 ranked by the number of distinct project repositories on which they were reported. 
The table shows: the number of times each exception was reported as 
the root cause of a stack trace, the number of distinct projects reporting such causes on stack traces, 
and the percentages of such in relation to all reported exceptions and analyzed projects respectively.
It also presents the whether the method responsible for signaling the exceptions were
part of Android, the application itself, libcore, or a third-party library as presented in Table  \ref{tab:signalers} 
 \footnote{Nine exception stack traces contained only elements of JVM and were discarded from the analysis}.

@@

\begin{table*}
  \centering
  \begin{tabular}{rcccccccc}
    \hline
    \bfseries{Root Exception} &  \multicolumn{2}{c}{\bfseries{Projects (GH/CG)}} &  \multicolumn{2}{c}{\bfseries{Occurrences (GH/CG)}} & \textsf{Android} & \textsf{Libcore} & \textsf{App} & \textsf{Lib} \\
    & \bfseries{\#} &  \bfseries{\%} & \bfseries{\# } & \bfseries{\% } &&&&\\
    \hline
java.lang.NullPointerException            & 254 /  78  & 52,70\%  & 1225 / 439  & 30,08\% & 473 /  26  & 18 /  & 595 / 241 & 137 / 169 \\  %LIBORAPP=408
java.lang.IllegalStateException          & 99 / 21  & 20,54\%  & 234 / 44  & 5,75\%  & 165 / 15 & 12  / 0 & 36  / 5 & 20 / 24  \\
java.lang.IllegalArgumentException          & 94 / 48  & 19,50\% & 255 / 98  & 6,26\% & 146 / 41 & 6 / 0 & 64 / 31  & 39  / 26  \\
java.lang.RuntimeException                & 91 / 31 & 18,88\% & 232 / 87  & 5,70\%  & 167 / 33 & 1 / 0 & 47 / 17 & 17 / 37   \\
java.lang.OutOfMemoryError                 & 56  / 22  & 11,62\% & 180 / 57 & 4,42\% & 121 / 18 & 15 / 0 & 17 / 18  & 23 / 13  \\
java.lang.NoClassDefFoundError           & 52  / 15 & 10,79\%  & 73 / 21   & 1,79\%  & 9 / 1   & 0 / 0  & 37 / 9  & 26 / 11   \\
java.lang.ClassCastException             & 49  / 15 & 10,17\%  & 94 / 36   & 2,31\%  & 43 / 3  & 0  / 0 & 40 / 15  & 11 / 18  \\
java.lang.IndexOutOfBoundsException       & 47  / 15 & 9,75\%   & 127 / 39  & 3,12\% & 47 / 2  & 0/0  & 71/22  & 8 / 14    \\
java.lang.NoSuchMethodError               & 40 / 14  & 8,30\%  & 57 / 23  & 1,40\%  & 9  /  0  & 0  / 0 & 39 /  17    & 9 / 6  \\
java.util.ConcurrentModificationException & 38 / 5 & 7,88\% & 54 / 11  & 1,33\%   & 5  / 0  & 0  / 0 & 43 / 3 & 6 / 7  \\

    \hline
  \end{tabular}
\caption{Root Exceptions occurrences and popularity.}
\label{tab:toptenandroid}
\end{table*}

@@

\begin{table}
  \centering
  \begin{tabular}{lrr}
    \hline
    \bfseries{Category} &  \bfseries{\% reported on stacks} \\
    \hline
      Programming logic (java.lang and util) &  52,0\%\\ 
      Resources (IO, Memory, Batery)       &   23,9\% \\ 
      Security                               &  4,1\%\\  
      Concurrency                            &  2,9\% \\ 
      Backward compatibility                 & 5,5\% \\ 
      Specific Exceptions               &  4,9\%\\ 
      General (Error, Exception, Runtime)    &  6,7\%\\
  \end{tabular}
  \caption{Characterization of the 100 root causes.}
  \label{tab:tophundrend}
\end{table}

@@

@@

Runtime	&	1075 / 160	&	56 	&	1446 / 397	&	374	/  386  &	2951 / 943\\
Error	       &	 144	 / 32              &	34	&	168	 / 134               &	105	 / 74           &	451 /  240	\\
Checked	&	110	   / 39           &	230	&	139	  / 174            &	145	 / 466           &	624  /  679	\\
Throwable	&	0 /0	       &	0	&	1 / 1	             &	0	     / 0               &	1 / 1	\\
Undefined	&	1 / 1 	&	0	&	6 / 	12		&	8	/ 32	   &	15 / 45	\\ %22 DISTINCT EXCEPTIONS AND 9 IN GIT
    \hline
All		& 1330	&	320	&	1760	&	632	&	4042	\\
    \hline
  \end{tabular}
\caption{Types of root exceptions.}
  \label{tab:typeroottab}
\end{table}

@@

Consequently, since it is not expected by the programmer, when such method throws 
this exception, such undocumented exception may remain
uncaught and cause the app to crash, or may be mistakenly handled by subsumption - 
The exception stack traces reporting this scenario is actually a real bug of Android 
Gingerbread version (which still accounts for 13.6% of devices running Android).

@@

>>>>

\author{\IEEEauthorblockN{Roberta Coelho\IEEEauthorrefmark{1},
Lucas Almeida\IEEEauthorrefmark{1},
Georgios Gousios\IEEEauthorrefmark{2}, 
Arie van Deursen\IEEEauthorrefmark{2}
}
\IEEEauthorblockA{\IEEEauthorrefmark{1}Federal University of Rio Grande do Norte\\
Natal, Brazil\\
Email: \texttt{roberta@dimap.ufrn.br,lucas.almeida@ppgsc.ufrn.br}}
\IEEEauthorblockA{\IEEEauthorrefmark{2}Delft University of Technology\\
Delft, The Netherlands\\
Email: \texttt{\{g.gousios,arie.vandeursen\}@tudelft.nl}}
}

@@

This paper reports a repository mining study which analyzed all the issues created on
Android projects available in GitHub (482 applications) and Google code (157 applications)
Overall, our research set includes 32,582 issues in GitHub and 41,674 issues in Googlecode 
from which 6,005 exception stack traces were extracted. Such stack traces were distilled and analyzed in 
combination with source code and bytecode analysis. This study 
consistently identifies common characteristics of reported 
exception stacks traces - e.g., the NullPointerException was the reported cause 
on 30,08\% of all analyzed exception stack traces, and was mentioned in approximately 
50\% of all projects analyzed. Moreover,  the cross-project analysis 
of exception stack traces enabled to consistently reveal   
fragilities of the exception-related code: 
(1) undocumented runtime exceptions signaled by third party code,
(2) undocumented checked exceptions thrown by Android native code
(3) unexpected exception wrappings (e.g., Errors being wrapped in checked exceptions) 
revealing that Java hybrid exception model is not fully used according to its purpose.
Such fragilities impose challenges to application robustness not only 
in Android environment but also to other systems based on Java exception model.

@@

%482 applications) and Google code (157 applications)

To do so we perform a post mortem analysis of the exception stack traces embedded on all issues
created on Android projects available in GitHub and Googlecode. Using a custom tool called ExceptionMiner,
 which we develop specifically for this study, we mine stack traces from issues across all Android projects on
GitHub and Googlecode. Overall, we analyzed all issues extracted from on 482 Android projects defined in
GitHub and 157 projects defined in Googlecode. Overall it corresponds to 74,256 issues (32,582 issues from GitHub projects 
and 41,674 issues from Googlecode projects) from which  6,005 stack traces were extracted and used as
 a source of information for our analysis. The stack trace analysis was augmented by additional information
extracted from JDK, Android SO and Android SDK and the applications using byte code and source code analysis.
 Manual inspection was used to leverage the understanding of exception stack traces and support further discussions and insights.

@@

%4,208

This set of 482 projects contained overall 32,582 issues from which 4,042 exception stack traces 
were extracted. Issues on Github are different from issues on dedicated bug tracking tools such as 
Bugzilla and Jira. The most important difference is that there are no predefined fields
  (e.g. severity and priority). Instead, Github uses a more open ended tagging system, on which
repositories are offered a pre-defined set of labels, but repository owners can modify 
them at will. Therefore, an issue may have none ore an arbitrary set of labels depending 
on which repository it was created.

@@

To identify Android projects in Googlecode, we performed a similar heuristic, we performed a case insensitive search 
(on Googlecode search interface) for the term \textsf{android}.  On January 2014, when we queried Googlecode, such heuristic could
 find 788  projects, from which 724 defined at least 1 issue and, 183 projects 
had at least one issue including a stack trace. Then we performed further cleanup, inspecting the site of every Android
reporting at least one stack trace, and as a result we could identify 157. 
Android projects.  All issues created on such projects (i.e., 41,674 issues) were analyzed and 1,963 stack traces 
were extracted.

@@

\noindent\emph{Exception Stack Trace Distiller.} 
Distills the information that composes a stack trace and storing the results in a
relational database. Some of the information extracted from the stack traces were:
 the exception being thrown, its signaler, the exception root cause, its corresponding signaler,
and packages related to each one of these fields.
The tool is based on a combination between a regular expression based parser 
with heuristics able to identify and filter exception names and stack traces inline with text. In
contrast to existing issue parsing solutions such as Infozilla, the parser
created in this work can discover stack traces embedded in logs files \footnote{In several 
exception stack traces, the exception frames were preceeded by logging information e.g., "03-01 15:55:01.609 (7924): at android.app.ActivityThread.access\$600(ActivityThread.java:127)" which could not be detected by existing tools.)}  
and identify the root causes and signalers associated to each exception stack trace.

@@

\subsection{Manual Inspections}
This study was also based in a set of manual inspection tasks. Besides the 
 identification of Android projects details previously. 
Manual inspections were used discover the type of exceptions thrown by 
the applications and libraries we manually inspect the sourcecode or javadoc
 documentation of each of them. When the exception was removed from the 
last app version, the previous versions were analyzed. When the exception was
 not found on the previous versions, the exception was discarded.  Only 31 exceptions 
remained undefined - such exceptions were reported on 61 exception stack traces as 
presented in Table ~\ref{tab:typeroottab}.

@@

After distilling the information available on the exception stack traces we could find 
the the exceptions commonly reported as the root causes of stack traces.
Table \ref{tab:toptenandroid} illustrates the top 10 root causes found in the study,
 ranked by the number of distinct project repositories on which they were reported. 
The table shows: the number of times each exception was reported as 
the root cause of a stack trace, the number of distinct projects reporting such causes on stack traces, 
and the percentages of such in relation to all reported exceptions and analyzed projects respectively.
It also presents the whether the method responsible for signaling the exceptions were
part of Android, the application itself, libcore, or a third-party library as presented in Table  \ref{tab:signalers}

% \footnote{Nine exception stack traces contained only elements of JVM and were discarded from the analysis}.

@@

%java.lang.NullPointerException            & 254 /  78  & 52,70\%  & 1225 / 439  & 30,08\% & 473 /  26  & 18 /  & 595 / 241 & 137 / 169 \\  %LIBORAPP=408
%java.lang.IllegalStateException          & 99 / 21  & 20,54\%  & 234 / 44  & 5,75\%  & 165 / 15 & 12  / 0 & 36  / 5 & 20 / 24  \\
%java.lang.IllegalArgumentException          & 94 / 48  & 19,50\% & 255 / 98  & 6,26\% & 146 / 41 & 6 / 0 & 64 / 31  & 39  / 26  \\
%java.lang.RuntimeException                & 91 / 31 & 18,88\% & 232 / 87  & 5,70\%  & 167 / 33 & 1 / 0 & 47 / 17 & 17 / 37   \\
%java.lang.OutOfMemoryError                 & 56  / 22  & 11,62\% & 180 / 57 & 4,42\% & 121 / 18 & 15 / 0 & 17 / 18  & 23 / 13  \\
%java.lang.NoClassDefFoundError           & 52  / 15 & 10,79\%  & 73 / 21   & 1,79\%  & 9 / 1   & 0 / 0  & 37 / 9  & 26 / 11   \\
%java.lang.ClassCastException             & 49  / 15 & 10,17\%  & 94 / 36   & 2,31\%  & 43 / 3  & 0  / 0 & 40 / 15  & 11 / 18  \\
%java.lang.IndexOutOfBoundsException       & 47  / 15 & 9,75\%   & 127 / 39  & 3,12\% & 47 / 2  & 0/0  & 71/22  & 8 / 14    \\
%java.lang.NoSuchMethodError               & 40 / 14  & 8,30\%  & 57 / 23  & 1,40\%  & 9  /  0  & 0  / 0 & 39 /  17    & 9 / 6  \\
%java.util.ConcurrentModificationException & 38 / 5 & 7,88\% & 54 / 11  & 1,33\%   & 5  / 0  & 0  / 0 & 43 / 3 & 6 / 7  \\

%java.lang.IllegalStateException          & 99 / 21  & 20,54\%  & 234 / 44  & 5,75\%  & 165 / 15 & 12  / 0 & 36  / 5 & 20 / 24  \\
%java.lang.IllegalArgumentException          & 94 / 48  & 19,50\% & 255 / 98  & 6,26\% & 146 / 41 & 6 / 0 & 64 / 31  & 39  / 26  \\
%java.lang.RuntimeException                & 91 / 31 & 18,88\% & 232 / 87  & 5,70\%  & 167 / 33 & 1 / 0 & 47 / 17 & 17 / 37   \\
%java.lang.OutOfMemoryError                 & 56  / 22  & 11,62\% & 180 / 57 & 4,42\% & 121 / 18 & 15 / 0 & 17 / 18  & 23 / 13  \\
%java.lang.NoClassDefFoundError           & 52  / 15 & 10,79\%  & 73 / 21   & 1,79\%  & 9 / 1   & 0 / 0  & 37 / 9  & 26 / 11   \\
%java.lang.ClassCastException             & 49  / 15 & 10,17\%  & 94 / 36   & 2,31\%  & 43 / 3  & 0  / 0 & 40 / 15  & 11 / 18  \\
%java.lang.IndexOutOfBoundsException       & 47  / 15 & 9,75\%   & 127 / 39  & 3,12\% & 47 / 2  & 0/0  & 71/22  & 8 / 14    \\
%java.lang.NoSuchMethodError               & 40 / 14  & 8,30\%  & 57 / 23  & 1,40\%  & 9  /  0  & 0  / 0 & 39 /  17    & 9 / 6  \\
%java.util.ConcurrentModificationException & 38 / 5 & 7,88\% & 54 / 11  & 1,33\%   & 5  / 0  & 0  / 0 & 43 / 3 & 6 / 7  \\
%
%java.lang.NullPointerException	&	254	/	78	&	52,70\%	&	1225	/	439	&	30,08\%	&	473	/	52	&	18	/	2	&	595	/	241	&	137	/	143	\\	%LIBORAPP=408
%java.lang.IllegalStateException	&	99	/	21	&	20,54\%	&	234	/	44	&	5,75\%	&	165	/	20	&	12	/	19	&	36	/	5	&	20	/	19		\\
%java.lang.IllegalArgumentException	&	94	/	48	&	19,50\%	&	255	/	98	&	6,26\%	&	146	/	49	&	6	/	6	&	64	/	31	&	18	/	26		\\
%java.lang.RuntimeException	&	91	/	31	&	18,88\%	&	232	/	87	&	5,70\%	&	167	/	36	&	1	/	1	&	47	/	17	&	17	/	34		\\
%java.lang.OutOfMemoryError	&	56	/	22	&	11,62\%	&	180	/	57	&	4,42\%	&	121	/	20	&	15	/	1	&	17	/	18	&	23	/	11		\\
%java.lang.NoClassDefFoundError	&	52	/	15	&	10,79\%	&	73	/	21	&	1,79\%	&	9	/	1	&	0	/	0	&	37	/	9	&	26	/	11		\\
%java.lang.ClassCastException	&	49	/	15	&	10,17\%	&	94	/	36	&	2,31\%	&	43	/	12	&	0	/	0	&	40	/	15	&	11	/	9		\\
%java.lang.IndexOutOfBoundsException	&	47	/	15	&	9,75\%	&	127	/	39	&	3,12\%	&	47	/	6	&	0		0	&	71	/	22	&	8	/	10		\\
%java.lang.NoSuchMethodError	&	40	/	14	&	8,30\%	&	57	/	23	&	1,40\%	&	9	/	1	&	0	/	0	&	39	/	17	&	9	/	5		\\
%java.util.ConcurrentModificationException	&	38	/	5	&	7,88\%	&	54	/	11	&	1,33\%	&	5	/	0	&	0	/	0	&	43	/	3	&	6	/	7

\begin{table*}
  \centering
  \begin{tabular}{rcccccccc}
    \hline
    \bfseries{Root Exception} &  \multicolumn{2}{c}{\bfseries{Projects (GH\&CG)}} &  \multicolumn{2}{c}{\bfseries{Occurrences (GH\&CG)}} & \textsf{Android} & \textsf{Libcore} & \textsf{App} & \textsf{Lib} \\
    & \bfseries{\#} &  \bfseries{\%} & \bfseries{\# } & \bfseries{\% } &&&&\\
    \hline

java.lang.NullPointerException	&	332	&	51,96\%	&	1664	&	27,71\%	&	525	&	20	&	836	&	280	\\
java.lang.IllegalStateException	&	120	&	18,78\%	&	278	&	4,63\%	&	185	&	31	&	41	&	39	\\
java.lang.IllegalArgumentException	&	142	&	22,22\%	&	353	&	5,88\%	&	195	&	12	&	95	&	44	\\
java.lang.RuntimeException	&	122	&	19,09\%	&	319	&	5,31\%	&	203	&	2	&	64	&	51	\\
java.lang.OutOfMemoryError	&	78	&	12,21\%	&	237	&	3,95\%	&	141	&	16	&	35	&	34	\\
java.lang.NoClassDefFoundError	&	67	&	10,49\%	&	94	&	1,57\%	&	10	&	0	&	46	&	37	\\
java.lang.ClassCastException	&	64	&	10,02\%	&	130	&	2,16\%	&	55	&	0	&	55	&	20	\\
java.lang.IndexOutOfBoundsException	&	62	&	9,70\%	&	166	&	2,76\%	&	53	&	0	&	93	&	18	\\
java.lang.NoSuchMethodError	&	54	&	8,45\%	&	80	&	1,33\%	&	10	&	0	&	56	&	14	\\
java.util.ConcurrentModificationException	&	43	&	6,73\%	&	65	&	1,08\%	&	5	&	0	&	46	&	13	\\
\\

    \hline
  \end{tabular}
\caption{Root Exceptions occurrences and popularity in repositories hosted in Googlecode (GC) and GitHub(GH).}
\label{tab:toptenandroid}
\end{table*}

@@

\begin{table}
  \centering
  \begin{tabular}{lrr}
    \hline
    \bfseries{Category} &  \bfseries{\% Occurrences on stacks} \\
    \hline
      Programming logic (java.lang and util) &  52,0\%\\ 
      Resources (IO, Memory, Batery)       &   23,9\% \\ 
      Security                               &  4,1\%\\  
      Concurrency                            &  2,9\% \\ 
      Backward compatibility                 & 5,5\% \\ 
      Specific Exceptions               &  4,9\%\\ 
      General (Error, Exception, Runtime)    &  6,7\%\\
  \end{tabular}
  \caption{Characterization of the 100 root causes.}
  \label{tab:tophundrend}
\end{table}

@@

% \bfseries{Root Cause Type} & \bfseries{Android} & \bfseries{Libcore} & \bfseries{App} & \bfseries{Lib}  & \bfseries{All}\\
% Runtime	&	1075 / 260	&	56  / 17	&	1446 / 397	&	374	/  316  &	2951 / 943\\
%Error	       &	 144	 / 44              &	34 / 12	&	168	 / 134              &	105	 / 62           &	451 /  240	\\
%Checked	&	193	/ 83            &	230 / 84	&	139	  / 174          &	145 / 422	           &	624  / 734	\\
%Throwable	&	0 /0	       &	0	&	1 / 1	             &	0	     / 0               &	1 / 1	\\
%Undefined	&	1 / 3 	&	0	&	6 / 	12		&	8 / 30	   &	15 / 45	\\ %22 DISTINCT EXCEPTIONS AND 9 IN GIT

%Runtime	&	1075 / 160	&	56 	&	1446 / 397	&	374	/  386  &	2951 / 943\\
%Error	       &	 144	 / 32              &	34	&	168	 / 134               &	105	 / 74           &	451 /  240	\\
%Checked	&	110	   / 39           &	230	&	139	  / 174            &	145	 / 466           &	624  /  679	\\
%Throwable	&	0 /0	       &	0	&	1 / 1	             &	0	     / 0               &	1 / 1	\\
%Undefined	&	1 / 1 	&	0	&	6 / 	12		&	8	/ 32	   &	15 / 45	\\ %22 DISTINCT EXCEPTIONS AND 9 IN GIT
%All		& 1330	&	320	&	1760	&	632	&	4042	\\

%Runtime	&	1235	&	56 	&	1843	&	760  &	3894\\
%Error	       &	 176              &	34	&	302               &	179          &	691	\\
%Checked	&	149           &	230	&	313            &	611           &	1303	\\
%Throwable	&	0        &	0	&	2             &	0	                    &	2	\\
%Undefined	&	2 	&	0	&	18		& 40	   &	60	\\ %22 DISTINCT EXCEPTIONS AND 9 IN GIT
%  \hline
%All		& 1562	& 320	& 	2478	& 1590	& 5950 \\

%FILTRAR LIBCODE:
%FILTRO ANDROID: 74 (com.android) 122(com.google)
%SELECT REPO, main_signaler, *
%  FROM stacktracesummary where mainsignaler_from='LIB_or_APP' AND main_signaler like 'com.google%' ;

@@

Runtime	&	1335	&	73	&	1843	&	690  &	3894\\
Error	       &	 188              &	 46	&	302             &	167	           &	691	\\
Checked	&	276           &	314	&	313          &	567	           &	1358	\\
Throwable	&	0	       &	0	&	2            &	0	     / 0               &	2	\\
Undefined	&	4	&	0	&	18		&	38	   &	60	\\
 \hline
All		& 1803	&	433	&	2478	&	1462	&	6005	\\
    \hline
  \end{tabular}
\caption{Types of root exceptions.}
  \label{tab:typeroottab}
\end{table}

@@

Consequently, since it is not expected by the programmer, when such method throws 
this exception, such undocumented exception may remain
uncaught and cause the app to crash, or may be mistakenly handled by subsumption - 
The exception stack traces reporting this scenario is actually a real bug of Android 
Gingerbread version (which still accounts for 13.6\% of devices running Android).

Among the Android projects on which this exception stack trace was reported we can cite:
PageTurner (206 stars, 130 forks, 1184 commits), ActionBarSherlock (6,041 stars, 
3,436 forks, and 1479 commints), otto (1,618 stars,	342 forks, 	177 commints).

%SELECT repo, *
% FROM stacktracesummary where stack like '%getDeclaredMethods%';

@@

TODO: ATUALIZAR DISCUSSAO COM BASE NOS NOVOS DADOS.
